Data Preparation

### 2019-01-25 Data Preparation.Rmd

```{r clean grade variable}
d_transcript <- d_transcript %>%
  mutate(Grade = case_when(Grade == "NG"~ "-1",
                           T~ Grade),
          Grade = str_replace(string = Grade, pattern = ",",replace = "."),
         Grade = as.numeric(Grade))
```

@@

# Save Data
```{r}
save(lists, d_course, d_AoD, d_assessment, d_transcript,
     file = "data_pillar_1.RDATA")
save(lists, d_course, d_AoD, d_assessment, d_transcript,
     d_overview, d_description, d_manual,
     file = "data_pillar_2.RDATA")
```

>>>>

```{r clean grade variable}
d_transcript <- d_transcript %>%
  mutate(Grade = case_when(Grade == "NG" ~ "NA",
                           TRUE          ~ Grade),
         Grade = str_replace(string = Grade, pattern = ",",replace = "."),
         Grade = as.numeric(Grade)) %>%
  filter(!is.na(Grade)) %>%
  mutate(Fail = Grade < 5.5)
```

@@

# Save Data
```{r}
save(lists, d_course, d_AoD, d_assessment, d_transcript,
     file = "Output/data_pillar_1.RDATA")
save(lists, d_course, d_AoD, d_assessment, d_transcript,
     d_overview, d_description, d_manual,
     file = "Output/data_pillar_2.RDATA")
```
